Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-10-22 Ben_Manuscripts/stochastic_transport/Draft.tex
Anomalous diffusion analysis

  We modeled the distributions of hop lengths in two ways. First, we assumed the 
  distribution to be Gaussian since it is possible to exactly simulate realizations of
  fractional Brownian motion. Second, we fit the distributions to L\'evy stable 
  distributions since it is more general than the Gaussian distribution. We plotted
  the MLE fits of both on top of urea's hop length distribution in 
  Figure~\ref{fig:hop_distribution_comparison}. The L\'evy distribution does a better
  job capturing the heavy tails and high density near 0 of the hop length distribution.
  However, since there are no known exact simulation techniques for generating 
  realizations of fractional L\'evy motion, we must explore whether this more general
  fit is worthwhile.

  We also modeled the distribution of dwell times in two ways. First, we assumed pure
  power law behavior since it is consistent with most theoretical descriptions of CTRWs.
  The data fits well to this model at short dwell times but
  the density of long dwell times is over-estimated. In our second approach, we truncate
  the power law distribution with an exponential cut-off, lowering the probability of
  long dwell times. We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where the
  density of the truncated power law drops below that of the pure power law and tends towards
  0 near a dwell time of 250 ns.

  The model parameters for the 1 and 2 mode models are tabulated in 
  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} respectively 
  and tell their own story about each solute's behavior. 
%  Using the techniques 
%  from Section~\ref{method:model_sFBM}, we extracted parameter values for each
%  solute in order to create 1 and 2 mode models, displayed in Tables~\ref{table:sfbm_params} 
%  and~\ref{table:sfbm_params_2mode} respectively. 
  Higher values of $\sigma$ and lower
  values of $\alpha_h$ indicate larger average hop length magnitudes by increasing the
  hop length distribution's width and tail density respectively. Higher values of $\alpha_d$
  indicate a lower probability of long dwell times. Higher values of $\lambda$ truncate
  the power law distribution earlier preventing extremely long dwell times. Values of $H$
  closer to the Brownian limit of 0.5, indicate a lower degree of negative correlation 
  between hops. All of which contribute to an overall increase in the MSD.

  The parameters of the 1 mode model indicate some diversity in solute behavior. The value
  of $\alpha_d$ for pure and truncated power law fits to the dwell time distributions of 
  urea, ethylene glycol and methanol are similar. The value of $\alpha_d$ for acetic
  acid is significantly lower than the rest of the solutes meaning it stays trapped 
  for long periods of time more frequently. The value of $\lambda$ is largest for
  methanol indicating that its longest dwell time is shorter than the longest dwell
  times of all other solutes. When hops are fit to a Gaussian, it is clear that acetic
  acid takes the smallest hops while methanol takes the largest. If we fit hops to a
  L\'{e}vy stable distribution, we observe a similar trend in $\sigma$ values, but 
  with varying weights on the distribution's tails. Acetic acid has the heaviest
  tails (lowest $\alpha_h$), meaning it is more likely to take large hops, while 
  ethylene glycol stays close to a Gaussian distribution (i.e. $\alpha_h$ near 2).
  The Hurst parameters indicate a moderate degree of anti-correlation between hops. 
  Surprisingly, methanol takes the most anti-correlated hops (lowest $H$). This is
  likely because methanol spends the largest fraction of its time within the pores. 
  It can still make large hops thanks to its small size, but tends to bounce around
  the tails.

  The difference in parameters of each mode of the 2 mode sFBM model offer additional
  mechanistic insight which the 1 mode model lacks. It is clear that solutes are 
  significantly slowed while they are in the tail region (mode 2) where long dwell times
  are more probable and hops are smaller (smaller $\alpha_d$). 
% BJC: I'm not sure how valid it is to analyze lambda because it is dependent on alpha. There is some counterbalancing going on.  
% The values of $\lambda$, however, do not 
% appear to be directly correlated to mode. For example, $\lambda$ for ethylene glycol is
% lower in the pores, meaning its longest dwell times in the pores are longer than its
% longest dwell times in the tails. This may be a consequence of    
  Interestingly, $\alpha_h$ for urea and acetic acid in mode 2 is 1.50 meaning its 
  hop distribution is heavy tailed relative to ethylene glycol and methanol whose 
  $\alpha_h$ values are more consistent with a Gaussian distribution. Acetic acid and
  urea are structurally similar molecules, both planar with two heavy atoms attached to
  a carbonyl group. Their small size and rigid shape may allow them to slip through 
  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
  larger jumps to escape traps.

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  \multicolumn{7}{|c|}{2 Mode Model} \\\hline
                & Parameters                               & Mode & Urea         & Ethylene Glycol &  Methanol    & Acetic Acid \\
  \hline
                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           & 0.92         & 0.58         \\\cline{3-7}
  Dwell         &                                          & 2    & 0.38         &  0.48           & 0.58         & 0.33         \\\cline{2-7}
  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   & 1.07, 0.0005 & 0.41, 0.0026 \\\cline{3-7}
                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   & 0.32, 0.0049 & 0.00, 0.0021 \\\hline
                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           & 0.43         & 0.32         \\\cline{3-7}
  Hop           &                                          & 2    & 0.24         &  0.23           & 0.32         & 0.17         \\\cline{2-7}
  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     & 0.28, 1.87   & 0.21, 1.91   \\\cline{3-7}
                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     & 0.20, 1.80   & 0.09, 1.50   \\\hline
  Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           & 0.30         & 0.34         \\\cline{3-7}
  \hline 
  \end{tabular}
  %MRS4: more about what the consequences of these results are?
  \caption{To create a 2 mode model, we generated a set of parameters based on solute
  behavior as function of distance from the pore center. Mode 1 corresponds to solute
  behavior within 0.75 nm of the pore center and mode 2 corresponds to behavior greater
  than or equal to 0.75 nm from the pore center. Note that we used the same Hurst parameter
  for both modes due to a low number of sufficiently long sequences of hops in each mode. 
  See Table~\ref{table:sfbm_params} for descriptions of the parameters.}\label{table:sfbm_params_2mode}
  \end{table}

  Our models can reasonably predict the MD simulated MSDs. Using the parameters in 
  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} as inputs, we compared
  the MSD of simulated anomalous diffusion trajectories to MD simulated MSDs. The MSD
  curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs
  for comparison in Figures~\ref{fig:anomalous_msds_1mode} and 
  Figure~\ref{fig:anomalous_msds_2mode} respectively.

@@

  Truncating the power laws with an exponential cut-off has the largest effect on the on 
  the match between MD MSD and simulated anomalous diffusion trajectories. Without 
  truncation, the MD MSDs are underestimated. This is because dwell times on the order 
  of the MD simulation length are sampled and incorporated into the simulated anomalous
  diffusion trajectories, reducing the MSD. The longest observed dwell time among the
  solutes was 1.3 $\mu$s by ethylene glycol.

  %BJC3: simulated anomalous diffusion --> SAD ? HMM kind of a downer
  Simulated anomalous diffusion trajectories which draw from a L\'evy stable distribution
  generally predict higher MSDs. The heavy tails of the distribution incorporate large
  jumps more frequently into the trajectories. The only exception is that of ethylene
  glycol in the 2 mode model where the L\'evy index for both modes is near 2, indicating
  a near Gaussian distribution, but the MLE of the $\sigma$ values of the L\'evy stable
  distribution are much smaller than the Gaussian MLE $\sigma$ values.
  %BJC3: I need to investigate this. How could sigma be so far underestimated if basically Gaussian

  % BJC3: I'd like to present the parameter values because they give clues
  % towards mechanisms
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|c|c|c|c|c|}
%  \hline
%  \multirow{4}{*}{Model} & \multicolumn{4}{c|}{Urea} \\\cline{2-5}
%  & \multicolumn{4}{c|}{Single Mode (H = 0.37)} \\\cline{2-5}
%  & \multicolumn{2}{c|}{Dwells} & \multicolumn{2}{c|}{hops} \\\cline{2-5}
%  & $\alpha$ & $\lambda$ & $\sigma$ & $\alpha$ \\\hline
%  sFBM   & 0.57 & --     & 0.33 & --   \\
%  sFBMcut& 0.40 & 0.0024 & 0.33 & --   \\
%  sFLM   & 0.57 & --     & 0.21 & 1.84 \\
%  sFLMcut& 0.40 & 0.0024 & 0.21 & 1.84 \\
%  \hline
%  \end{tabular}
%  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
%  trajectories and then computed the average ensemble-averaged MSD of 10000 
%  simulated trajectories.}\label{table:sfbm_params}
%  \end{table}

%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
%  \hline
%  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol & Methanol & Acetic Acid \\
%  \hline
%  Dwell         & $P(\alpha_d)$             & 0.57         & & & \\
%  Distributions & $P_T(\alpha_d, \lambda)$  & (0.4, 0.0024)& & & \\
%  \hline
%  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & & & \\
%  Distributions & $L(\sigma, \alpha_h)$     & (0.21, 1.84) & & & \\
%  \hline
%  Correlation   & $\gamma(H)$               & 0.37         & & & \\
%  \hline 
%  \end{tabular}
%  \caption{To create a 1 mode model for each solute, we parameterized a pure power
%  law ($P(\alpha_d)$) and a truncated power law $P_T(\alpha_d, \lambda)$ distribution 
%  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
%  law tails and higher values of $\lambda$ truncate the distribution at lower
%  dwell times. We parameterized Gaussian ($\mathcal{N}$) and L\'evy stable 
%  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
%  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
%  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
%  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
%  function ($\gamma(H)$) to describe the degree of correlation between hops. 
%  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
%  \end{table}
%  
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
%  \hline
%  2 Mode Model  & Parameters                               & Mode & Urea         & Ethylene Glycol & Methanol & Acetic Acid \\
%  \hline
%                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.57         & & & \\\cline{3-7}
%  Dwell         &                                          & 2    & 0.57         & & & \\\cline{2-7}
%  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    &(0.4, 0.0024) & & & \\\cline{3-7}
%                &                                          & 2    &(0.4, 0.0024) & & & \\\hline
%                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.33         & & & \\\cline{3-7}
%  Hop           &                                          & 2    & (0.21, 1.84) & & & \\\cline{2-7}
%  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.33         & & & \\\cline{3-7}
%                &                                          & 2    & (0.21, 1.84) & & & \\\hline
%  \multirow{2}{*}{Correlation}&\multirow{2}{*}{$\gamma(H)$}& 1    & 0.37         & & & \\\cline{3-7}
%                &                                          & 2    & 0.37         & & & \\\cline{3-7}
%  \hline 
%  \end{tabular}
%  \caption{To create a 2 mode model, we generated a set of parameters based on solute
%  behavior as function of distance from the pore center. Mode 1 corresponds to solute
%  behavior within 0.75 nm of the pore center and mode 2 corresponds to behavior greater
%  than or equal to 0.75 nm from the pore center. See Table~\ref{table:sfbm_params}
%  for descriptions of the parameters.}\label{table:sfbm_params_2mode}
%  \end{table}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{|M{1.75cm}|M{1.65cm}|M{2cm}|M{2cm}|M{2cm}|M{2cm}|}
  \hline
  \multirow{2}{*}{Solute}&\multirow{2}{*}{Model}& \multicolumn{2}{c|}{Trained on First Half} & \multicolumn{2}{c|}{Trained on Second Half}        \\\cline{3-6}
                              &        & MSD                     & Prediction & MSD                 & Prediction \\\hline
  \multirow{2}{*}{Urea}       & sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
                              & sFLMcut&                         &            &                     &            \\\hline
  Ethylene                    & sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
  Glycol                      & sFLMcut&                         &            &                     &            \\\hline
  \multirow{2}{*}{Methanol}   & sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
                              & sFLMcut&                         &            &                     &            \\\hline
  \multirow{2}{*}{Acetic Acid}& sFBMcut&\multirow{2}{*}{}        &            &\multirow{2}{*}{}    &            \\\cline{2-2}\cline{4-4}\cline{6-6}
                              & sFLMcut&                         &            &                     &            \\\hline
  \end{tabular}
  \caption{}\label{table:sFBM_train}
  \end{table}

@@

  To create an MSDDM for each solute, we generated emission distributions based 
  on transitions from each state and transitions between states. There are not
  enough consecutive observations of each type of transition with which to study
  their individual correlation structures so we grouped all transition distributions
  into a single distribution and measured the correlation of the series of all 
  transitions. We lose information about individual types of transitions however, 
  we believe this is unavoidable without at least an order of magnitude of additional data.

  We observe correlated emissions drawn from L\'evy stable distributions.
  The deviation of the emission distributions from Gaussian behavior is far more pronounced
  than that seen in the hop length distributions of the previous section, therefore we 
  did not consider the Gaussian case (see Figure~\ref{fig:gaussian_levy_comparison}).
  The correlation structure between hops resembles that of FLM (Figure~\ref{fig:msddm_acf}).
  The parameters of the L\'evy stable distributions along with their Hurst parameters 
  are tabulated in Table~\ref{table:msddm_params}. 
  %MRS4: might this work better visually?  Table in SI, figure here?
  %BJC4: like a bar plot?
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
  \caption{}\label{fig:gaussian_levy_comparison}
  \end{subfigure}
  % /figures/msddm_acf.py
  \begin{subfigure}{0.42\textwidth}
  \includegraphics[width=\textwidth]{msddm_acf.pdf}
  \caption{}\label{fig:msddm_acf}
  \end{subfigure}
  \caption{(a) Emission distributions are non-Gaussian and heavy-tailed. Shown here is the
  emission distribution for transitions between states. The maximum likelihood
  Gaussian fit severely underestimates the empirical density of hops near and far from zero 
  while overestimating the density of hops at intermediate values. (b) Jumps drawn from
  the transition distribution are negatively correlated to each other. The normalized version 
  of Equation~\ref{eqn:flm_autocovariance} fits well to the data suggesting FLM is
  an appropriate way to model jumps.} \label{fig:msddm_emissions}
  \end{figure}

>>>>

  We modeled the distributions of hop lengths in two ways. First, we assumed the 
  distribution to be Gaussian since it is possible to exactly simulate realizations of
  fractional Brownian motion. Second, we fit the distributions to L\'evy stable 
  distributions since it is more general than the Gaussian distribution. We plotted
  the MLE fits of both on top of urea's hop length distribution in 
  Figure~\ref{fig:hop_distribution_comparison}. The L\'evy distribution does a better
  job capturing the heavy tails and high density near 0 of the hop length distribution.
  However, since there are no known exact simulation techniques for generating 
  realizations of fractional L\'evy motion, we must evaluate whether this more general
  fit is worthwhile.

  We also modeled the distribution of dwell times in two ways. First, we assumed pure
  power law behavior since it is consistent with most theoretical descriptions of CTRWs.
  The data fits well to this model at short dwell times but the density of long dwell
  times is over-estimated. In our second approach, we truncate the power law distribution
  with an exponential cut-off, lowering the probability of extremely long dwell times. 
  We demonstrate this effect in the inset to Figure~\ref{fig:powerlaw}, where the
  density of the truncated power law drops below that of the pure power law and tends towards
  0 near a dwell time of 250 ns.

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  \multicolumn{7}{|c|}{2 Mode Model} \\\hline
                & Parameters                               & Mode & Urea         & Ethylene Glycol &  Methanol    & Acetic Acid \\
  \hline
                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           & 0.90         & 0.58         \\\cline{3-7}
  Dwell         &                                          & 2    & 0.38         &  0.48           & 0.58         & 0.33         \\\cline{2-7}
  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   & 1.04, 0.0006 & 0.41, 0.0026 \\\cline{3-7}
                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   & 0.30, 0.0054 & 0.00, 0.0021 \\\hline
                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           & 0.45         & 0.32         \\\cline{3-7}
  Hop           &                                          & 2    & 0.24         &  0.23           & 0.32         & 0.17         \\\cline{2-7}
  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     & 0.31, 1.97   & 0.21, 1.91   \\\cline{3-7}
                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     & 0.20, 1.85   & 0.09, 1.50   \\\hline
  Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           & 0.30         & 0.34         \\\cline{3-7}
  \hline 
  \end{tabular}
  \caption{The two model parameterizes solute behavior in the pores and tails separately. 
  Generally, movement is much more restricted in the tail region. To create a 2 mode model,
  we generated a set of parameters based on solute behavior as function of distance from
  the pore center. Mode 1 corresponds to solute behavior within 0.75 nm of the pore center
  and mode 2 corresponds to behavior greater than or equal to 0.75 nm from the pore center.
  Note that we used the same Hurst parameter for both modes due to a low number of 
  sufficiently long sequences of hops in each mode. See Table~\ref{table:sfbm_params} for
  descriptions of the parameters.}\label{table:sfbm_params_2mode}
  \end{table}

  Using the parameters in Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}
  as inputs to our models, we obtain reasonable predictions of the MD simulated MSDs. The 
  MSD curves generated from 1 and 2 mode models are overlayed with the MD simulated MSDs for 
  comparison in Figures~\ref{fig:anomalous_msds_1mode} and Figure~\ref{fig:anomalous_msds_2mode}
  respectively. Our anomalous diffusion trajectories have a significantly reduced 
  uncertainty and lie well within the error bars of MD.

@@

  Truncating the power laws with an exponential cut-off has the largest effect on the on 
  the match between the MD-calculated MSD and that measured from the simulated anomalous
  diffusion trajectories. Without truncation, the MD MSDs are underestimated in all cases.
  This is because dwell times on the order of the MD simulation length are sampled and 
  incorporated into the simulated anomalous diffusion trajectories, reducing the MSD. 
  The longest observed dwell time among the solutes was 1.3 $\mu$s by ethylene glycol.

  %BJC3: simulated anomalous diffusion --> SAD ? HMM kind of a downer
  Simulated anomalous diffusion trajectories which draw from a L\'evy stable distribution
  generally predict higher MSDs. The heavy tails of the distribution incorporate large
  jumps more frequently into the trajectories. The only exception is that of ethylene
  glycol in the 2 mode model where the L\'evy index for both modes is near 2, indicating
  a near Gaussian distribution.

  The model parameters for the 1 and 2 mode models tell stories about each solute's behavior. 
  Higher values of $\sigma$ and lower values of $\alpha_h$ indicate larger average 
  hop length magnitudes by increasing the hop length distribution's width and tail 
  density respectively. Higher values of $\alpha_d$ indicate a lower probability of 
  long dwell times. Higher values of $\lambda$ truncate the power law distribution 
  earlier preventing extremely long dwell times. Values of $H$ closer to the Brownian
  limit of 0.5, indicate a lower degree of negative correlation between hops. All 
  of which contribute to an overall increase in the MSD.

  Turning first to the parameters of the 1 mode model, we can begin to break down the
  trends in solute MSDs. The parameters belonging to ethylene glycol and methanol are
  relatively similar which is consistent with their similar MD-measured MSDs. Methanol 
  tends to stay trapped for less time and takes larger hops but the most substantial
  difference is with respect to their Hurst parameters. In fact, methanol has the lowest
  $H$ of all the solutes studied. It is possible that we have underestimated $H$ since 
  it appears that our model consistently under-predicts the methanol MSD curve relative
  to other solutes. However, it remains plausible that methanol does have a low $H$ 
  value because it spends the majority of its time outside the pore region where collisions
  with tails are frequent. Urea has the third highest MSD which is influenced primarily
  by more frequent and long dwell times, indicated by lower values of $\alpha_d$ and 
  $\lambda$. Urea's hop lengths ($\sigma$) and correlation ($H$) are comparable to ethylene
  glycol and methanol. Acetic acid has the smallest MSD among the solutes studied due 
  to longer periods of entrapment and shorter hops. Its trapping behavior is parameterized
  by an $\alpha_d$ value significantly lower than other solutes, but an intermediate 
  $\lambda$ value, suggesting it experiences many medium length periods of entrapment. 
  Its hops are smaller but are slightly compensated by a heavier tailed distribution 
  (lower $\alpha_h$) than the other solutes.

  We can use the 2 mode model to gain an even deeper understanding of solute behavior
  in the pore versus in the tails. It is clear that solutes are significantly slowed 
  while they are in the tail region (mode 2) where long dwell times are more probable
  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Interestingly, 
  $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
  structurally similar molecules, both planar with two heavy atoms attached to a 
  carbonyl group. Their small size and rigid shape may allow them to slip through 
  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
  larger jumps to escape traps.

%  The parameters of the 1 mode model indicate some diversity in solute behavior. The value
%  of $\alpha_d$ for pure and truncated power law fits to the dwell time distributions of 
%  urea, ethylene glycol and methanol are similar. The value of $\alpha_d$ for acetic
%  acid is significantly lower than the rest of the solutes meaning it stays trapped 
%  for long periods of time more frequently. The value of $\lambda$ is largest for
%  methanol indicating that its longest dwell time is shorter than the longest dwell
%  times of all other solutes. When hops are fit to a Gaussian, it is clear that acetic
%  acid takes the smallest hops while methanol takes the largest. If we fit hops to a
%  L\'{e}vy stable distribution, we observe a similar trend in $\sigma$ values, but 
%  with varying weights on the distribution's tails. Acetic acid has the heaviest
%  tails (lowest $\alpha_h$), meaning it is more likely to take large hops, while 
%  ethylene glycol stays close to a Gaussian distribution (i.e. $\alpha_h$ near 2).
%  The Hurst parameters indicate a moderate degree of anti-correlation between hops. 
%  Surprisingly, methanol takes the most anti-correlated hops (lowest $H$). This is
%  likely because methanol spends the largest fraction of its time within the pores. 
%  It can still make large hops thanks to its small size, but tends to bounce around
%  the tails.

%  The difference in parameters of each mode of the 2 mode sFBM model offer additional
%  mechanistic insight which the 1 mode model lacks. It is clear that solutes are 
%  significantly slowed while they are in the tail region (mode 2) where long dwell times
%  are more probable and hops are smaller (smaller $\alpha_d$). 
% BJC: I'm not sure how valid it is to analyze lambda because it is dependent on alpha. There is some counterbalancing going on.  
% The values of $\lambda$, however, do not 
% appear to be directly correlated to mode. For example, $\lambda$ for ethylene glycol is
% lower in the pores, meaning its longest dwell times in the pores are longer than its
% longest dwell times in the tails. This may be a consequence of    
%  Interestingly, $\alpha_h$ for urea and acetic acid in mode 2 is 1.50 meaning its 
%  hop distribution is heavy tailed relative to ethylene glycol and methanol whose 
%  $\alpha_h$ values are more consistent with a Gaussian distribution. Acetic acid and
%  urea are structurally similar molecules, both planar with two heavy atoms attached to
%  a carbonyl group. Their small size and rigid shape may allow them to slip through 
%  gaps in the tails. Meanwhile, methanol is small enough that it does not need to make 
%  larger jumps to escape traps.

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{|M{1.75cm}|M{1cm}|M{1.65cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|M{2.5cm}|}
  \hline
  \multirow{2}{*}{Solute}&\multirow{2}{*}{Modes}&\multirow{2}{*}{Model}&\multicolumn{2}{c|}{Trained on First Half} & \multicolumn{2}{c|}{Trained on Second Half}        \\\cline{4-7}
                              &                   &        & MD MSD                & Prediction & MD MSD               & Prediction \\\hline
  \multirow{4}{*}{Urea}       & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.43 (1.11, 1.76)}&0.31 (0.28, 0.35)&\multirow{4}{*}{1.43 (1.11, 1.77)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &            &                     &            \\\hline
                              & \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{1.03 (0.79, 1.29)}        &            &\multirow{4}{*}{1.03 (0.77, 1.30)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
  Ethylene                    &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
  Glycol                      &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &            &                     &            \\\hline
  \multirow{4}{*}{Methanol}   &\multirow{2}{*}{1} &sFBMcut&\multirow{4}{*}{1.06 (0.69, 1.36)}        &            &\multirow{4}{*}{1.06 (0.67, 1.37)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &            &                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
                              &\multirow{2}{*}{2} &sFBMcut&                         &            &                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &            &                     &            \\\hline
  \multirow{4}{*}{Acetic Acid}& \multirow{2}{*}{1}&sFBMcut&\multirow{4}{*}{0.35 (0.28, 0.45)}&0.31 (0.28, 0.35)&\multirow{4}{*}{0.35 (0.26, 0.47)}    &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &0.35 (0.30, 0.40)&                     &            \\\cline{2-3}\cline{5-5}\cline{7-7}
                              & \multirow{2}{*}{2}&sFBMcut&                         &0.23 (0.20, 0.27)&                     &            \\\cline{3-3}\cline{5-5}\cline{7-7}
                              &                   &sFLMcut&                         &            &                     &            \\\hline
  \end{tabular}
  \caption{}\label{table:sFBM_train}
  \end{table}

@@

  %BJC4: maybe some kind of transitional paragraph here.

  To create an MSDDM for each solute, we generated emission distributions for
  fluctuations within each state and transitions between states. There are not
  enough consecutive observations of each type of transition with which to study
  their individual correlation structures so we grouped all transition distributions
  into a single distribution and measured the correlation of the series of all 
  transitions. We lose information about individual types of transitions, however, 
  we believe this is unavoidable without at least an order of magnitude of additional data.

  We observe correlated emissions drawn from L\'evy stable distributions.
  The deviation of the emission distributions from Gaussian behavior is far more pronounced
  than that seen in the hop length distributions of the previous section, therefore we 
  did not consider the Gaussian case (see Figure~\ref{fig:gaussian_levy_comparison}).
  The correlation structure between hops resembles that of FLM (Figure~\ref{fig:msddm_acf}).
  The parameters of the L\'evy stable distributions along with their Hurst parameters 
  are tabulated in Table~\ref{table:msddm_params}. 
  %MRS4: might this work better visually?  Table in SI, figure here?
  %BJC4: Somehow I'd need to fit 108 pieces of data into a figure
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
  \caption{}\label{fig:gaussian_levy_comparison}
  \end{subfigure}
  % /figures/msddm_acf.py
  \begin{subfigure}{0.42\textwidth}
  \includegraphics[width=\textwidth]{msddm_acf.pdf}
  \caption{}\label{fig:msddm_acf}
  \end{subfigure}
  \caption{(a) Emission distributions are non-Gaussian and heavy-tailed. Shown here is the
  emission distribution for transitions between states. The maximum likelihood
  Gaussian fit severely underestimates the empirical density of hops near and far from zero 
  while overestimating the density of hops at intermediate values. (b) Jumps drawn from
  the transition distribution are negatively correlated to each other. The normalized version 
  of Equation~\ref{eqn:flm_autocovariance} fits well to the data suggesting FLM is
  an appropriate way to model jumps.} \label{fig:msddm_emissions}
  \end{figure}
